### 2021-10-26 README.Rmd
sfsdfsf

Windows users will invariably have to install it since it will not come by default. [*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) and installer to do this. Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users. Afterward, a simple `choco install make` command should work just fine. The increased integration of Linux into Windows, prominently [Windows Subsystem for Linux](https://docs.microsoft.com/en-us/windows/wsl/install-win10), offers more avenues for Windows users to install Make on their operating system.

>>>>

Windows users will invariably have to install it since it will not come by default. [*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) and installer to do this. Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users. Afterward, a simple `choco install make` command should work just fine. The increased integration of Linux into Windows, prominently [Windows Subsystem for Linux](https://docs.microsoft.com/en-us/windows/wsl/install-win10), offers more avenues for Windows users to install Make on their operating system. I thank [Dave Braze](https://github.com/davebraze) for alerting me to another option. Windows users can install and configure `make` through installing `{RTools}`. Afterwards, the user can add a fully qualified path to their PATH environment. You can [read more about this process here](https://cran.r-project.org/bin/windows/Rtools/).
